Unsupervised Semantic Mapping for Healthcare Data Storage Schema

### 2021-06-05 ManuScript/IEEEAccess/submission 0/source/ManuScript.tex
key word setting

\begin{keywords}
Context aware systems, Decision support systems, Electronic medical records,Experts systems,   Health information management, Medical information systems, Ontology engineering, Text processing, Unsupervised learning
\end{keywords}

>>>>

\begin{keywords}
Context awareness, Decision support systems, Expert systems, Health information management, Medical information systems, Ontology engineering, Text processing, Unsupervised learning
\end{keywords}
